On the surprising effectiveness of a simple matrix exponential derivative approximation, with application to global SARS-CoV-2

### 2023-10-25 manuscript/revision_letter.tex
right before sending to collabs

To the Editor and Reviewers:

@@

In particular, we have:
\begin{itemize}
	\item clarified how the present work relates to our other work that includes thorough simulation studies \citet{magee2023random} and provides strong theoretical guarantees for surrogate-trajectory HMC \citet{glatt2020accept};

	\item implemented an additional simulation study which compares accuracy for multiple algorithms, different model sizes and different signal strength regimes;

@@

\begin{reply}
	Thank you for the opportunity to submit a revised manuscript. We have made ample additions to the manuscript in response to the suggestions made by both reviewers. Among the many improvements we have made to this manuscript, the simulation study suggested by Reviewer 2 helps the paper smoothly transition between theory and application.
\end{reply}

@@

\begin{reply}
  It is important to note that surrogate-trajectory HMC using approximate gradients provides the exact same theoretical guarantees as regular HMC.  The two algorithms generate transition kernels that leave the targeted posterior distribution invariant.  \cite{glatt2020accept} provides a deep measure theoretic rationale for why this is the case.  Perhaps because of these theoretical guarantees, we did not emphasize this in the original manuscript.

>>>>

Dear Editor and Reviewers:

@@

In particular, we have:
\begin{itemize}
	\item clarified how the present work relates to our other work that includes thorough simulation studies \citep{magee2023random} and provides strong theoretical guarantees for surrogate-trajectory HMC \citep{glatt2020accept};

	\item implemented two additional simulation studies which compare posteriors obtained for multiple algorithms and illustrate parameter identification  for different model sizes and different sparsity regimes;

@@

\begin{reply}
	Thank you for the opportunity to submit a revised manuscript. We have made ample additions to the manuscript in response to the helpful suggestions made by both reviewers. Among the many improvements we have made to this manuscript, the simulation studies suggested by Reviewer 2 help the paper smoothly transition between theory and application.
\end{reply}

@@

\begin{reply}
  It is important to note that surrogate-trajectory HMC using approximate gradients provides the exact same theoretical guarantees as regular HMC.  The two algorithms generate transition kernels that leave the targeted posterior distribution invariant.  \cite{glatt2020accept} provides a deep measure theoretic rationale for why this is the case.  Perhaps because of these theoretical guarantees, we did not emphasize such a comparison in the original manuscript.
